A Way Forward in Parallelising Dynamic Languages

### 2014-06-03 talk/icooolps2014/position-paper.tex
Add a comment

We believe that further work to reduce the overhead of STM is
very worthwhile. In fact, considering some analogies that have been
drawn between garbage collection and transactional memory~\cite{dan07},
we believe that it is worthwhile to focus the STM research more
specifically on the context shown in this paper --- for use in
implementations of high-level languages, rather than as a tool
directly used by the programmer.

>>>>

We believe that further work to reduce the overhead of STM is
very worthwhile. In fact, considering some analogies that have been
drawn between garbage collection and transactional memory~\cite{dan07},
we believe that it is worthwhile to focus the STM research more
specifically onto the context shown in this paper --- for use in
implementations of high-level languages, rather than as a tool
directly used by the programmer.
